Supporting Information : Effect of copula on extinction risk

### 2019-02-27 SuppMat.Rmd
several changes, Table added

```{r fig_agestr_with_extremetail_linear, echo=F,results="hide"}
xL<-las_exL$extdf[1:26,]
xR<-las_exR$extdf[1:26,]
t<-c(0:(nrow(xL)-1))
pdf(paste("./Results/age_str_results/extrisk_age_str_extremetail_linear.pdf",sep=""),height=6,width=6)
op<-par(mar=c(4,4,2,2),mgp=c(2.5,0.5,0))
plot(0,-1,ylim=c(0,1),xlim=range(t),ylab="Extinction risk",xlab="time",cex.lab=1.5)
x<-xL
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(1,0,0,0.3), border = NA)
lines(t,x$erA,col="red",type="l")
x<-xR
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(0,0,1,0.3), border = NA)
lines(t,x$erA,col="blue",type="l")
legend("topleft", c("Left tail","Right tail"), lty=c(1,1),  
       col=c('red', 'blue'), horiz=F, bty='n', cex=1.2)
par(op)
dev.off()
```

@@

```{r fig_agestr_with_extremetail_nonlinear, echo=F,results="hide"}
xL<-nlas_exL$extdf[1:26,]
xR<-nlas_exR$extdf[1:26,]
t<-c(0:(nrow(xL)-1))
pdf(paste("./Results/age_str_results/extrisk_age_str_extremetail_nonlinear_omg_",omg,".pdf",sep=""),height=6,width=6)
op<-par(mar=c(4,4,2,2),mgp=c(2.5,0.5,0))
plot(0,-1,ylim=c(0,1),xlim=range(t),ylab="Extinction risk",xlab="time",cex.lab=1.5)
x<-xL
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(1,0,0,0.3), border = NA)
lines(t,x$erA,col="red",type="l")
x<-xR
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(0,0,1,0.3), border = NA)
lines(t,x$erA,col="blue",type="l")
legend("topleft", c("Left tail","Right tail"), lty=c(1,1),  
       col=c('red', 'blue'), horiz=F, bty='n', cex=1.2)
par(op)
dev.off()
```

@@

for(i in c(1:length(rlist))){
    r<- rlist[i]
    params<-c(r,K)
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,plotteron = F,resloc=resloc,checkon=F,getacf=F)

    temp_mat<-cbind(s$d_seq,s$risk_left,s$risk_right,s$pop_avg_acf_left,s$pop_avg_acf_right)
    res_ricker_local<-abind(res_ricker_local,temp_mat,along = 3)

@@

for(r in rlist){
    #cat("r=",r,"\n")
    params<-c(r,K)
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,plotteron = F,resloc=resloc,checkon=F,getacf=F)

    temp_mat<-cbind(s$d_seq,s$risk_left,s$risk_right,s$pop_avg_acf_left,s$pop_avg_acf_right)
    res_ricker_global<-abind(res_ricker_global,temp_mat,along = 3)
}

@@

for(i in 1:dim(res_ricker_local)[3]){
  #s<-res_ricker_local[,,i]
  s<-res_ricker_local[,,i][1:6,] # plot for d in range (0 to 0.5)
  s<-as.data.frame(s)

  plot(s$d,s$risk_left,xlim=range(s$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  #legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
  #       col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
  #---------------------------------------------------
  ## Allow a second plot on the same graph
  #par(new=TRUE)

@@

for(i in 1:dim(res_ricker_global)[3]){
  #s<-res_ricker_global
  s<-res_ricker_global[,,i][1:6,] # plot for d in range (0 to 0.5)
  s<-as.data.frame(s)

  plot(s$d,s$risk_left,xlim=range(s$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  #legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
  #       col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
}
par(op)
dev.off()
```

@@

for(i in c(1:length(rlist))){
    r<- rlist[i]
    K_e<-((r^(1/b))-1)/a
    ext_thrs<-K_e/10
    params<-c(r,a,b)
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,plotteron = F,resloc=resloc,checkon=F,getacf=F)

    temp_mat<-cbind(s$d_seq,s$risk_left,s$risk_right,s$pop_avg_acf_left,s$pop_avg_acf_right)
    res_hassell_local<-abind(res_hassell_local,temp_mat,along = 3)

    hassell_extrisk_d0$risk_left_d0[i]<-s$risk_left[1]
    hassell_extrisk_d0$risk_right_d0[i]<-s$risk_right[1]
}

@@

# For global dispersion
res_hassell_global<-c()
for(r in rlist){
    #cat("r=",r,"\n")
    K_e<-((r^(1/b))-1)/a
    ext_thrs<-K_e/10
    params<-c(r,a,b)
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,plotteron = F,resloc=resloc,checkon=F,getacf=F)

    temp_mat<-cbind(s$d_seq,s$risk_left,s$risk_right,s$pop_avg_acf_left,s$pop_avg_acf_right)
    res_hassell_global<-abind(res_hassell_global,temp_mat,along = 3)
}
anm<-paste("r_",rlist,sep="")
cnm<-c("d","risk_left","risk_right","pop_avg_acf_left","pop_avg_acf_right")
dimnames(res_hassell_global)<-list(NULL,cnm,anm)
saveRDS(res_hassell_global,paste(resloc,"res_hassell_global.RDS",sep=""))
```

@@

for(i in 1:dim(res_hassell_local)[3]){
  s<-res_hassell_local[,,i][1:6,] # plot for d in range (0 to 0.5)
  s<-as.data.frame(s)

  plot(s$d,s$risk_left,xlim=range(s$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  #legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
  #       col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
}
par(op)
dev.off()

@@

for(i in 1:dim(res_hassell_global)[3]){
  s<-res_hassell_global[,,i][1:6,] # plot for d in range (0 to 0.5)
  s<-as.data.frame(s)

  plot(s$d,s$risk_left,xlim=range(s$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  #legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
  #       col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
}
par(op)
dev.off()
```

@@

for(i in c(1:length(rlist))){
    r<- rlist[i]
    params<-c(r,a,b)
    K_e<-((r-1)^(1/b))/a
    ext_thrs<-K_e/10
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,plotteron = F,resloc=resloc,checkon=F,getacf=F)

    temp_mat<-cbind(s$d_seq,s$risk_left,s$risk_right,s$pop_avg_acf_left,s$pop_avg_acf_right)
    res_msmith_local<-abind(res_msmith_local,temp_mat,along = 3)

    msmith_extrisk_d0$risk_left_d0[i]<-s$risk_left[1]
    msmith_extrisk_d0$risk_right_d0[i]<-s$risk_right[1]
}

@@

# For global dispersal in D matrix 
res_msmith_global<-c()
for(r in rlist){
    #cat("r=",r,"\n")
    params<-c(r,a,b)
    K_e<-((r-1)^(1/b))/a
    ext_thrs<-K_e/10
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,plotteron = F,resloc=resloc,checkon=F,getacf=F)

    temp_mat<-cbind(s$d_seq,s$risk_left,s$risk_right,s$pop_avg_acf_left,s$pop_avg_acf_right)
    res_msmith_global<-abind(res_msmith_global,temp_mat,along = 3)
}
anm<-paste("r_",rlist,sep="")
cnm<-c("d","risk_left","risk_right","pop_avg_acf_left","pop_avg_acf_right")
dimnames(res_msmith_global)<-list(NULL,cnm,anm)
saveRDS(res_msmith_global,paste(resloc,"res_msmith_global.RDS",sep=""))
```

@@

for(i in 1:dim(res_msmith_local)[3]){
  s<-res_msmith_local[,,i][1:6,] # plot for d in range (0 to 0.5)
  s<-as.data.frame(s)

  plot(s$d,s$risk_left,xlim=range(s$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  #legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
  #       col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
}
par(op)
dev.off()

@@

for(i in 1:dim(res_msmith_global)[3]){
  s<-res_msmith_global[,,i][1:6,] # plot for d in range (0 to 0.5)
  s<-as.data.frame(s)

  plot(s$d,s$risk_left,xlim=range(s$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  #legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
  #       col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
}
par(op)
dev.off()
```

@@

for(i in c(1:length(rlist))){
    r<- rlist[i]
    params<-c(r,a,b)
    K_e<-(b/a)*(a+log(r-1))
    ext_thrs<-K_e/10
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,plotteron = F,resloc=resloc,checkon=F,getacf=F)

    temp_mat<-cbind(s$d_seq,s$risk_left,s$risk_right,s$pop_avg_acf_left,s$pop_avg_acf_right)
    res_pennycuick_local<-abind(res_pennycuick_local,temp_mat,along = 3)

    pennycuick_extrisk_d0$risk_left_d0[i]<-s$risk_left[1]
    pennycuick_extrisk_d0$risk_right_d0[i]<-s$risk_right[1]
}
anm<-paste("r_",rlist,sep="")
cnm<-c("d","risk_left","risk_right","pop_avg_acf_left","pop_avg_acf_right")
dimnames(res_pennycuick_local)<-list(NULL,cnm,anm)

@@

# For global dispersal in D matrix 
res_pennycuick_global<-c()
for(r in rlist){
    #cat("r=",r,"\n")
    params<-c(r,a,b)
    K_e<-(b/a)*(a+log(r-1))
    ext_thrs<-K_e/10
    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,plotteron = F,resloc=resloc,checkon=F,getacf=F)

    temp_mat<-cbind(s$d_seq,s$risk_left,s$risk_right,s$pop_avg_acf_left,s$pop_avg_acf_right)
    res_pennycuick_global<-abind(res_pennycuick_global,temp_mat,along = 3)
}
anm<-paste("r_",rlist,sep="")
cnm<-c("d","risk_left","risk_right","pop_avg_acf_left","pop_avg_acf_right")
dimnames(res_pennycuick_global)<-list(NULL,cnm,anm)
saveRDS(res_pennycuick_global,paste(resloc,"res_pennycuick_global.RDS",sep=""))
```

@@

for(i in 1:dim(res_pennycuick_local)[3]){
  s<-res_pennycuick_local[,,i][1:6,] # plot for d in range (0 to 0.5)
  s<-as.data.frame(s)

  plot(s$d,s$risk_left,xlim=range(s$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  #legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
  #       col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
}
par(op)
dev.off()

@@

for(i in 1:dim(res_pennycuick_global)[3]){
  s<-res_pennycuick_global[,,i][1:6,] # plot for d in range (0 to 0.5)
  s<-as.data.frame(s)

  plot(s$d,s$risk_left,xlim=range(s$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(s$d,s$risk_right,type="b",col="blue")
  #legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
  #       col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
}
par(op)
dev.off()
```

@@

    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=p0,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,plotteron = F,resloc=resloc,checkon=F,getacf=F)

    temp_mat<-cbind(s$d_seq,s$risk_left,s$risk_right,s$pop_avg_acf_left,s$pop_avg_acf_right)
    res_verhulst_local<-abind(res_verhulst_local,temp_mat,along = 3)

    verhulst_extrisk_d0$risk_left_d0[i]<-s$risk_left[1]
    verhulst_extrisk_d0$risk_right_d0[i]<-s$risk_right[1]
}

@@

    s<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=p0,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,plotteron = F,resloc=resloc,checkon=F,getacf=F)

    temp_mat<-cbind(s$d_seq,s$risk_left,s$risk_right,s$pop_avg_acf_left,s$pop_avg_acf_right)
    res_verhulst_global<-abind(res_verhulst_global,temp_mat,along = 3)
}
anm<-paste("r_",rlist,sep="")
cnm<-c("d","risk_left","risk_right","pop_avg_acf_left","pop_avg_acf_right")
dimnames(res_verhulst_global)<-list(NULL,cnm,anm)
saveRDS(res_verhulst_global,paste(resloc,"res_verhulst_global.RDS",sep=""))
```

@@

for(i in 1:dim(res_verhulst_local)[3]){
  s<-res_verhulst_local[,,i][1:6,] # plot for d in range (0 to 0.5)
  s<-as.data.frame(s)

>>>>

```{r fig_agestr_with_extremetail_linear, echo=F,results="hide"}
xL<-las_exL$extdf[1:26,]
xR<-las_exR$extdf[1:26,]
t<-c(0:(nrow(xL)-1))
pdf(paste("./Results/age_str_results/extrisk_age_str_extremetail_linear.pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(0,-1,ylim=c(0,1),xlim=range(t),ylab="Extinction risk",xlab="time",cex.lab=2,cex.axis=1.5)
x<-xL
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(1,0,0,0.3), border = NA)
lines(t,x$erA,col="red",type="l")
x<-xR
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(0,0,1,0.3), border = NA)
lines(t,x$erA,col="blue",type="l")
legend("topleft", c("vital rates : LTdep.","vital rates : RTdep."), lty=c(1,1),  
       col=c('red', 'blue'), horiz=F, bty='n', cex=1.5)
par(op)
dev.off()
```

@@

```{r fig_agestr_with_extremetail_nonlinear, echo=F,results="hide"}
xL<-nlas_exL$extdf[1:26,]
xR<-nlas_exR$extdf[1:26,]
t<-c(0:(nrow(xL)-1))
pdf(paste("./Results/age_str_results/extrisk_age_str_extremetail_nonlinear_omg_",omg,".pdf",sep=""),height=5,width=5)
op<-par(mar=c(5,4,1.5,1.5),mgp=c(2,0.7,0))
plot(0,-1,ylim=c(0,1),xlim=range(t),ylab="Extinction risk",xlab="time",cex.lab=2,cex.axis=1.5)
x<-xL
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(1,0,0,0.3), border = NA)
lines(t,x$erA,col="red",type="l")
x<-xR
polygon(c(rev(t), t), c(rev(x$CI0.975), x$CI0.025), col = rgb(0,0,1,0.3), border = NA)
lines(t,x$erA,col="blue",type="l")
legend("topleft", c("vital rates : LTdep.","vital rates : RTdep."), lty=c(1,1),  
       col=c('red', 'blue'), horiz=F, bty='n', cex=1.5)
par(op)
dev.off()
```

@@

for(i in c(1:length(rlist))){
    r<- rlist[i]
    params<-c(r,K)
    ss<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,plotteron = F,resloc=resloc, getacf=F)

    temp_mat<-cbind(ss$d_seq,ss$risk_left,ss$risk_right,ss$pop_avg_acf_left,ss$pop_avg_acf_right)
    res_ricker_local<-abind(res_ricker_local,temp_mat,along = 3)

@@

for(r in rlist){
    #cat("r=",r,"\n")
    params<-c(r,K)
    ss<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,plotteron = F,resloc=resloc, getacf=F)

    temp_mat<-cbind(ss$d_seq,ss$risk_left,ss$risk_right,ss$pop_avg_acf_left,ss$pop_avg_acf_right)
    res_ricker_global<-abind(res_ricker_global,temp_mat,along = 3)
}

@@

for(i in 1:dim(res_ricker_local)[3]){
  #s<-res_ricker_local[,,i]
  ss<-res_ricker_local[,,i][1:6,] # plot for d in range (0 to 0.5)
  ss<-as.data.frame(ss)

  plot(ss$d,s$risk_left,xlim=range(ss$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  liness(s$d,ss$risk_right,type="b",col="blue")
  #legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
  #       col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
  #---------------------------------------------------
  ## Allow a second plot on the same graph
  #par(new=TRUE)

@@

for(i in 1:dim(res_ricker_global)[3]){
  #s<-res_ricker_global
  ss<-res_ricker_global[,,i][1:6,] # plot for d in range (0 to 0.5)
  ss<-as.data.frame(ss)

  plot(ss$d,ss$risk_left,xlim=range(ss$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(ss$d,ss$risk_right,type="b",col="blue")
  #legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
  #       col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
}
par(op)
dev.off()
```

@@

for(i in c(1:length(rlist))){
    r<- rlist[i]
    K_e<-((r^(1/b))-1)/a
    ext_thrs<-K_e/10
    params<-c(r,a,b)
    ss<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,plotteron = F,resloc=resloc, getacf=F)

    temp_mat<-cbind(ss$d_seq,ss$risk_left,ss$risk_right,ss$pop_avg_acf_left,ss$pop_avg_acf_right)
    res_hassell_local<-abind(res_hassell_local,temp_mat,along = 3)

    hassell_extrisk_d0$risk_left_d0[i]<-ss$risk_left[1]
    hassell_extrisk_d0$risk_right_d0[i]<-ss$risk_right[1]
}

@@

# For global dispersion
res_hassell_global<-c()
for(r in rlist){
    #cat("r=",r,"\n")
    K_e<-((r^(1/b))-1)/a
    ext_thrs<-K_e/10
    params<-c(r,a,b)
    ss<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,plotteron = F,resloc=resloc, getacf=F)

    temp_mat<-cbind(ss$d_seq,ss$risk_left,ss$risk_right,ss$pop_avg_acf_left,ss$pop_avg_acf_right)
    res_hassell_global<-abind(res_hassell_global,temp_mat,along = 3)
}
anm<-paste("r_",rlist,sep="")
cnm<-c("d","risk_left","risk_right","pop_avg_acf_left","pop_avg_acf_right")
dimnames(res_hassell_global)<-list(NULL,cnm,anm)
saveRDS(res_hassell_global,paste(resloc,"res_hassell_global.RDS",sep=""))
```

@@

for(i in 1:dim(res_hassell_local)[3]){
  ss<-res_hassell_local[,,i][1:6,] # plot for d in range (0 to 0.5)
  ss<-as.data.frame(ss)

  plot(ss$d,ss$risk_left,xlim=range(ss$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(ss$d,ss$risk_right,type="b",col="blue")
  #legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
  #       col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
}
par(op)
dev.off()

@@

for(i in 1:dim(res_hassell_global)[3]){
  ss<-res_hassell_global[,,i][1:6,] # plot for d in range (0 to 0.5)
  ss<-as.data.frame(ss)

  plot(ss$d,ss$risk_left,xlim=range(ss$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(ss$d,ss$risk_right,type="b",col="blue")
  #legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
  #       col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
}
par(op)
dev.off()
```

@@

for(i in c(1:length(rlist))){
    r<- rlist[i]
    params<-c(r,a,b)
    K_e<-((r-1)^(1/b))/a
    ext_thrs<-K_e/10
    ss<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,plotteron = F,resloc=resloc, getacf=F)

    temp_mat<-cbind(ss$d_seq,ss$risk_left,ss$risk_right,ss$pop_avg_acf_left,ss$pop_avg_acf_right)
    res_msmith_local<-abind(res_msmith_local,temp_mat,along = 3)

    msmith_extrisk_d0$risk_left_d0[i]<-ss$risk_left[1]
    msmith_extrisk_d0$risk_right_d0[i]<-ss$risk_right[1]
}

@@

# For global dispersal in D matrix 
res_msmith_global<-c()
for(r in rlist){
    #cat("r=",r,"\n")
    params<-c(r,a,b)
    K_e<-((r-1)^(1/b))/a
    ext_thrs<-K_e/10
    ss<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,plotteron = F,resloc=resloc, getacf=F)

    temp_mat<-cbind(ss$d_seq,ss$risk_left,ss$risk_right,ss$pop_avg_acf_left,ss$pop_avg_acf_right)
    res_msmith_global<-abind(res_msmith_global,temp_mat,along = 3)
}
anm<-paste("r_",rlist,sep="")
cnm<-c("d","risk_left","risk_right","pop_avg_acf_left","pop_avg_acf_right")
dimnames(res_msmith_global)<-list(NULL,cnm,anm)
saveRDS(res_msmith_global,paste(resloc,"res_msmith_global.RDS",sep=""))
```

@@

for(i in 1:dim(res_msmith_local)[3]){
  ss<-res_msmith_local[,,i][1:6,] # plot for d in range (0 to 0.5)
  ss<-as.data.frame(ss)

  plot(ss$d,ss$risk_left,xlim=range(ss$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(ss$d,ss$risk_right,type="b",col="blue")
  #legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
  #       col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
}
par(op)
dev.off()

@@

for(i in 1:dim(res_msmith_global)[3]){
  ss<-res_msmith_global[,,i][1:6,] # plot for d in range (0 to 0.5)
  ss<-as.data.frame(ss)

  plot(ss$d,ss$risk_left,xlim=range(ss$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(ss$d,ss$risk_right,type="b",col="blue")
  #legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
  #       col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
}
par(op)
dev.off()
```

@@

for(i in c(1:length(rlist))){
    r<- rlist[i]
    params<-c(r,a,b)
    K_e<-(b/a)*(a+log(r-1))
    ext_thrs<-K_e/10
    ss<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,plotteron = F,resloc=resloc, getacf=F)

    temp_mat<-cbind(ss$d_seq,ss$risk_left,ss$risk_right,ss$pop_avg_acf_left,ss$pop_avg_acf_right)
    res_pennycuick_local<-abind(res_pennycuick_local,temp_mat,along = 3)

    pennycuick_extrisk_d0$risk_left_d0[i]<-ss$risk_left[1]
    pennycuick_extrisk_d0$risk_right_d0[i]<-ss$risk_right[1]
}
anm<-paste("r_",rlist,sep="")
cnm<-c("d","risk_left","risk_right","pop_avg_acf_left","pop_avg_acf_right")
dimnames(res_pennycuick_local)<-list(NULL,cnm,anm)

@@

# For global dispersal in D matrix 
res_pennycuick_global<-c()
for(r in rlist){
    #cat("r=",r,"\n")
    params<-c(r,a,b)
    K_e<-(b/a)*(a+log(r-1))
    ext_thrs<-K_e/10
    ss<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=K_e,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,plotteron = F,resloc=resloc, getacf=F)

    temp_mat<-cbind(ss$d_seq,ss$risk_left,ss$risk_right,ss$pop_avg_acf_left,ss$pop_avg_acf_right)
    res_pennycuick_global<-abind(res_pennycuick_global,temp_mat,along = 3)
}
anm<-paste("r_",rlist,sep="")
cnm<-c("d","risk_left","risk_right","pop_avg_acf_left","pop_avg_acf_right")
dimnames(res_pennycuick_global)<-list(NULL,cnm,anm)
saveRDS(res_pennycuick_global,paste(resloc,"res_pennycuick_global.RDS",sep=""))
```

@@

for(i in 1:dim(res_pennycuick_local)[3]){
  ss<-res_pennycuick_local[,,i][1:6,] # plot for d in range (0 to 0.5)
  ss<-as.data.frame(ss)

  plot(ss$d,ss$risk_left,xlim=range(ss$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(ss$d,ss$risk_right,type="b",col="blue")
  #legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
  #       col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
}
par(op)
dev.off()

@@

for(i in 1:dim(res_pennycuick_global)[3]){
  ss<-res_pennycuick_global[,,i][1:6,] # plot for d in range (0 to 0.5)
  ss<-as.data.frame(ss)

  plot(ss$d,ss$risk_left,xlim=range(ss$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(ss$d,ss$risk_right,type="b",col="blue")
  #legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
  #       col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
}
par(op)
dev.off()
```

@@

    ss<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=p0,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=F,plotteron = F,resloc=resloc, getacf=F)

    temp_mat<-cbind(ss$d_seq,ss$risk_left,ss$risk_right,ss$pop_avg_acf_left,ss$pop_avg_acf_right)
    res_verhulst_local<-abind(res_verhulst_local,temp_mat,along = 3)

    verhulst_extrisk_d0$risk_left_d0[i]<-ss$risk_left[1]
    verhulst_extrisk_d0$risk_right_d0[i]<-ss$risk_right[1]
}

@@

    ss<-varying_d(numsims=numsims,numsteps=numsteps,numlocs=numlocs,p0=p0,params=params,ext_thrs=ext_thrs,
                 scl=scl,model=model,disp_everywhere=T,plotteron = F,resloc=resloc, getacf=F)

    temp_mat<-cbind(ss$d_seq,ss$risk_left,ss$risk_right,ss$pop_avg_acf_left,ss$pop_avg_acf_right)
    res_verhulst_global<-abind(res_verhulst_global,temp_mat,along = 3)
}
anm<-paste("r_",rlist,sep="")
cnm<-c("d","risk_left","risk_right","pop_avg_acf_left","pop_avg_acf_right")
dimnames(res_verhulst_global)<-list(NULL,cnm,anm)
saveRDS(res_verhulst_global,paste(resloc,"res_verhulst_global.RDS",sep=""))
```

@@

for(i in 1:dim(res_verhulst_local)[3]){
  ss<-res_verhulst_local[,,i][1:6,] # plot for d in range (0 to 0.5)
  ss<-as.data.frame(ss)

  plot(ss$d,ss$risk_left,xlim=range(ss$d),ylim=c(0,1),type="b",col="red",
       #panel.first = grid(),
       xlab="d",ylab="Extinction risk",cex.lab=2,cex.axis=1.5)
  lines(ss$d,ss$risk_right,type="b",col="blue")
  #legend("bottomleft", c("noise : left","noise : right"), lty=c(1,1), pch=c(1,1), 
  #       col=c('red', 'blue'), horiz=T, bty='n', cex=1.2)
  mtext(paste0("r = ", round(rlist[i],5)),cex=1.2)
}
par(op)
dev.off()
